\documentclass[a4paper]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[font=normalsize,labelfont=bf]{caption}
\usepackage{balance}



\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


\begin{document}

% Opcion 1
\title{Dise침o e implementaci칩n de una central operativa para el control y monitoreo en el material rodante}


\author{

xxxxxx xxxxxxxxx, 
xxxxxxxx xxxxxxxx, 
xxxxx xxxxxxxxx \\

\normalsize \textit{xxxxxxx xxxxxxxx} \\
xxxxxxxxxxx xx xxxxxxxx xxxxxxxxx \\
\textit{xxxxxxxx xx xxxxxxxxxx - xxx} \\
\textit{xxxxxx xxxxx - xxxxxxxxx}
\textsuperscript{1}\small xxxxxxxxxxxxx \\

}


\maketitle

\input{sections/abstract_keywords}

\input{sections/motivation_context}

\input{sections/problematic}

\input{sections/proposed_architecture}

\input{sections/conclusions}

% \input{sections/references}


\balance
\begin{thebibliography}{00}

\bibitem{b1} 'Sistema de supervisi칩n de la seguridad del material
ferroviario utilizando patrones de dise침o', Ivan Mariano Di Vito, Pablo Gomez, Ariel Lutenberg, Libro de trabajos del CASE2019, Congreso Argetino de Sistemas Embebidos, Santa Fe, Argentina. (2019).

\bibitem{b2} CONICET-GICSAFe (June 2022). [Online]. Disponible: \\ https://sites.google.com/view/conicet-gicsafe/inicio

\bibitem{b3} Trenes Argentinos (June 2022). [Online]. Disponible: \\ https://www.argentina.gob.ar/transporte/trenes 

\bibitem{b4} 'Internet of Things for Measuring Human Activities in Ambient Assisted Living and e-Health', Amine Rghioui, Sendra Sandra, Lloret Jaime, Oumnad Abedlmajid,
Network Protocols and Algorithms. (2016).

\bibitem{b5} HTTP (June 2022). [Online]. Disponible: \\ https://developer.mozilla.org/es/docs/Web/HTTP 

\bibitem{b6} MQTT (June 2022). [Online]. Disponible: https://mqtt.org/ 

\bibitem{b7} QoS (June 2022). [Online]. Disponible: \\ https://www.hivemq.com/blog/mqtt-essentials-part-6-mqtt-quality-of-service-levels/

\bibitem{b8} NUCLEO-F429ZI (June 2022). [Online]. Disponible: \\ https://www.st.com/en/evaluation-tools/nucleo-f429zi.html

\bibitem{b9} Kafka (June 2022). [Online]. Disponible: https://kafka.apache.org/  

\bibitem{b10} 'TLS/SSL - MQTT Security Fundamentals' (2022). [Online]. \\ Disponible: https://www.hivemq.com/blog/mqtt-security-fundamentals-tls-ssl/ 

\bibitem{b11} X509 (June 2022). [Online]. Disponible: \\ https://www.ssl.com/faqs/what-is-an-x-509-certificate/ 

\bibitem{b12} Adversary-in-the-Middle (June 2022). [Online]. Disponible: \\ https://attack.mitre.org/techniques/T1557/

\bibitem{b13} PostgreSQL (June 2022). [Online]. Disponible: \\ https://www.postgresql.org/

\bibitem{b14} Kotlin (June 2022). [Online]. Disponible: https://kotlinlang.org/

\bibitem{b15} Ktor (June 2022). [Online]. Disponible: https://ktor.io/ 

\bibitem{b16} Hasura (June 2022). [Online]. Disponible: https://hasura.io/

\bibitem{b17} SQL (June 2022). [Online]. Disponible: https://www.w3schools.com/sql/

\bibitem{b18} API GraphQL (2022). [Online]. Disponible: https://graphql.org/

\bibitem{b19} TypeScript (June 2022). [Online]. Disponible: \\ https://www.typescriptlang.org/

\bibitem{b20} React (June 2022). [Online]. Disponible: https://reactjs.org/


\end{thebibliography}

\end{document}




